\begin{thebibliography}{99}
\addcontentsline{toc}{chapter}{References}
\bibitem{ref:Cisco}Cisco, ``Cisco Visual Networking Index: Global Mobile Data Traffic Forecast Update, 2014–2019,''Cisco White Paper.
\bibitem{ref:FCC}Federal Communications Commission, ``Spectrum policy task force report,fcc 02-155,'' Nov. 2002.
\bibitem{ref:mitola}J. Mitola III and G. Q. Maguire, Jr., ``Cognitive radio: making software radios more personal,'' IEEE Personal Communications, vol. 6, no. 4, pp. 13–18, Aug. 1999.
\bibitem{ref:Haykin} S. Haykin, ``Cognitive radio: Brain-empowered wireless communications,'' {\it IEEE J.Selected Areas Commun.},vol. 23, no. 2, pp. 201 - 220, Feb. 2005.
\bibitem{ref:MIC} Ministry of Internal Affairs and Communications, ``Japan Frequency Allocation Chart.'' http://www.tele.soumu.go.jp/resource/search/myuse/usecondition/wagakuni.pdf, accessed Jan. 15. 2016.
\bibitem{ref:fujii_Database} K. Sato, M. Kitamura, K. Inage, and T. Fujii, ``Measurement-based spectrum database for flexible spectrum management,'' IEICE Trans. Commun., vol.E98-B, no.10, pp.2004-2013, Oct. 2015.
\bibitem{ref:ON1}G. Zhou, J. Wu, K. Sohraby, ``Cooperative Spectrum Sensing with a Progressive MAP Detection Algorithm,'' Proc. GLOBECOM, pp.1-5, Dec. 2011.
\bibitem{ref:ON2}Y. Pei, Y. Liang, K.C.Teh, K. H. Li, ``Sensing-throughput tradeoff for cognitive radio networks: A multiple-channel sceario,'' Proc. IEEE PIMRC, pp.1257-1261, 13-16 Sept. 2009.
\bibitem{ref:quickest}L.Lai, Y.Fan, and H.V.Poor, ``Quickest Detection in Cognitive Radio: A Sequential Change Detection Framework,'' Proc. IEEE Globecom, Dec. 2008.
\bibitem{ref:overlay}Vameghestahbanati, M. and Mir, H.S. and El-Tarhuni, M., `` An overlay architecture for cognitive radio systems,'' Proc. IEEE ICCSPA, pp.1-4, Feb. 2014.
\bibitem{ref:underlay}H. Hu and Q. Zhu, ``Dynamic Spectrum Access in Underlay Cognitive Radio System with SINR Constraints,'' Proc. IEEE WiCompp. 1-4, Sept. 2009.
\bibitem{ref:fcc}Federal Communications Commission, SECOND MEMORANDUM OPINION AND ORDER, Sept. 2010.
\bibitem{ref:google}Google, ``Spectrum database.'' http://www.google.org/spectrum/whitespace/, accessed Jan. 15. 2016.
\bibitem{ref:microsoft}Microsoft, ``Microsoft Reserach White Space Finder'' http://whitespaces. cloudapp.net/, accessed Jan. 15. 2016.
\bibitem{ref:ED}T. Yucek and H. Arslan, ``A survey of spectrum sensing algorithms for cognitive radio applications,'' IEEE {\it Communications Surveys Tutorials}, vol. 11, no. 1, pp. 116-130, 2009.
\bibitem{ref:CUSUM}E. Page, ``Continuous inspection schemes,'' {\it Biometrika}, vol. 41, pp. 100-115, 1954.
\bibitem{ref:GLR}G. Lorden, ``Procedures for reacting to a change in distribution,'' {\it Annals of Mathematical Statistics}, vol. 42, no. 6, pp. 1897-1908, 1971.  
\bibitem{ref:threshold_cusum}G. Lorden, ``ON excess over the boundary,'' {\it Annals of Mathematical Statistics}, vol. 41, pp.520-527, Apr. 1970.
\bibitem{ref:threshold_GLR}G. Lorden, ``Open-ended tests for Koopman-Darmois families,'' {\it Annals of Statistics}, vol. 1, no. 4, pp. 520-527, Apr. 1970.
\end{thebibliography}
